---
title: "Model Averaging Marginal Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Model Averaging MArginal Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
MamarSingleStepforecast <- function(ts, num_lags, num_samples, step_forward=1,use_soft_max=F, bandwidth=0.5, kertype="normal"){
  len_ts <-  length(ts)
  enough_len <- T
  min_num_samples <- num_samples

  split_sample <- function(gap){
    x <- vector()
    y <- vector()
    i <- len_ts
    while (i-gap >= 1 && len_ts-i+1<= num_samples) {
      y = append(y,ts[i])
      x = append(x,ts[i-gap])
      i = i-1
    }
    if(i-gap==0 && len_ts-i+1<= num_samples){
      print("length of ts is not enough for num_samples samples")
      enough_len <- F
      min_num_samples = min(length(x),min_num_samples)
    }
    return(list(x=x,y=y))
  }

  kernel_model_set = list()
  n = min_num_samples
  X = matrix(0,n,num_lags)
  for (i in 1:n) {
    X[i,] = ts[(len_ts-step_forward-i+1) : (len_ts-step_forward-(num_lags-1)-i+1)]
  }
  Y = ts[len_ts:(len_ts-n+1)]

  for (gap in 1:num_lags) {
    temp = split_sample(gap+step_forward-1)
    exog = temp$x
    endog = temp$y
    kernel_model = ksmooth(x=exog,y=endog,kernel=kertype,bandwidth=bandwidth,x.points=c(exog,ts[len_ts-gap+1]))
    kernel_model_set = append(kernel_model_set,kernel_model[2])
  }
  M = matrix(0,n,num_lags)
  for(j in 1:num_lags){
    M[,j] = kernel_model_set[j]$y[1:n]
  }

  weight = tryCatch({
    solve(t(M) %*% M) %*% t(M) %*% Y
  }, error = function(e) {
    weight = rep(1/num_lags,num_lags)
  })

  if(use_soft_max){
    weight = exp(weight)/sum(exp(weight))
  }
  pred = vector()
  for(j in 1:num_lags){
    pred = append(pred,kernel_model_set[j]$y[n+1])
  }

  weight_pred = t(weight) %*% pred
  return(weight_pred)
}

MamarMultiStepforecast <- function(ts, num_lags, num_samples, max_forward_step=4, use_soft_max=F, bandwidth=0.5, kertype="normal"){
  res <- vector()
  for(t in 1:max_forward_step){
    res[t] = MamarSingleStepforecast(ts=ts, num_lags=num_lags, num_samples=num_samples, step_forward=t,use_soft_max=use_soft_max, bandwidth=bandwidth, kertype=kertype)
  }
  return(res)
}
```


## Basic Information
This is the introduction of my package \textbf{StatComp21091}. The main contribution of my package is to implement the Model Averaging MArginal Regression (MAMAR) algorithm proposed in the article: 
 
>Li D, Linton O, Lu Z. A flexible semiparametric forecasting model for time series[J]. Journal of Econometrics, 2015, 187(1): 345-357.
 
This algorithm basically approximate a multivariate regression function by an affine combination of one-dimensional marginal regression functions. 

## Method
See [Li D (2015)](https://www.sciencedirect.com/science/article/abs/pii/S0304407615000500)

## Usage
The \code{MamarSingleStepforecast()} function implement MAMAR algorithm to make single point forecasting of the input timeseries, with \code{num_lags} marginal regression models and last \code{num_samples} samples. For example, the following code make a one step forward forecast of \code{input_timeseries}:
```{r}
input_timeseries = rnorm(100)
pred <- MamarSingleStepforecast(ts=input_timeseries, num_lags=3, num_samples=50,step_forward=1)
```
and the result:
```{r}
print(pred)
```
Similarly, the \code{MamarMultiStepforecast()} function make multi-step forecast:
```{r}
multi_pred <- MamarMultiStepforecast(ts=input_timeseries, num_lags=3, 
                                     num_samples=50,max_forward_step = 7)
print(multi_pred)
```


